```{r}
library(tidyr)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(scales)
library(MASS)
library(lmtest)
library(psych)
library(moments)
library(tidyverse)
library(car)
library(cowplot)
library(olsrr)
library(caTools)
library(fastDummies)
```

```{r load the data}
clickstream_raw <- read.csv('e-shop clothing 2008.csv', sep =';', header = TRUE)
```

```{r}
names(clickstream_raw)
```
```{r}
head(clickstream_raw)
```

```{r rename columns and map categorical values}

clickstream <- clickstream_raw %>% 
        rename("sequence_click_in_session" = "order",
               "session_ID" = "session.ID",
               "product_category" = "page.1..main.category.",
               "product_code" = "page.2..clothing.model.",
               "product_color" = "colour",
               "product_location_on_page" = "location",
               "product_image_model_aspect" = "model.photography",
               "price_higher_than_avg" = "price.2",
               "page_of_product" = "page")

clickstream['product_location_vert'] <- clickstream['product_location_on_page']
clickstream['product_location_horiz'] <- clickstream['product_location_on_page']

clickstream <- clickstream %>%
  mutate(
    product_category = case_when(
      product_category == 1 ~ "Trousers",
      product_category == 2 ~ "Skirts",
      product_category == 3 ~ "Blouses",
      product_category == 4 ~ "Sale",
      TRUE ~ "Other"  # Default case
    ),
    product_image_model_aspect = case_when(
      product_image_model_aspect == 1 ~ "en face",
      product_image_model_aspect == 2 ~ "profile",
      TRUE ~ "Other"
    ),
    product_color = case_when(
      product_color == 1 ~ "beige",
      product_color == 2 ~ "black",
      product_color == 3 ~ "blue",
      product_color == 4 ~ "brown",
      product_color == 5 ~ "burgundy",
      product_color == 6 ~ "gray",
      product_color == 7 ~ "green",
      product_color == 8 ~ "navy blue",
      product_color == 9 ~ "of many colors",
      product_color == 10 ~ "olive",
      product_color == 11 ~ "pink",
      product_color == 12 ~ "red",
      product_color == 13 ~ "violet",
      product_color == 14 ~ "white",
      TRUE ~ "Other"
    ),
    price_higher_than_avg = case_when(
      price_higher_than_avg == 1 ~ "yes",
      price_higher_than_avg == 2 ~ "no",
      TRUE ~ "Other"
    ),
    product_location_horiz = case_when(
      product_location_horiz == 1 ~ "left",
      product_location_horiz == 2 ~ "middle",
      product_location_horiz == 3 ~ "right",
      product_location_horiz == 4 ~ "left",
      product_location_horiz == 5 ~ "middle",
      product_location_horiz == 6 ~ "left"
    ),
    product_location_vert = case_when(
      product_location_vert == 1 ~ "top",
      product_location_vert == 2 ~ "top",
      product_location_vert == 3 ~ "top",
      product_location_vert == 4 ~ "bottom",
      product_location_vert == 5 ~ "bottom",
      product_location_vert == 6 ~ "bottom"
    ),
    page_of_product = case_when(
      page_of_product == 1 ~ "first",
      page_of_product == 2 ~ "second",
      page_of_product == 3 ~ "third",
      page_of_product == 4 ~ "fourth",
      page_of_product == 5 ~ "fifth"
    )
    
  )

```


```{r Visualize distribution of each}
ggplot(clickstream, aes(x = factor(product_category))) +
  geom_bar() +
  xlab("Product Category") +
  ylab("Count") +
  ggtitle("Product Category Distribution")

ggplot(clickstream, aes(x = factor(product_image_model_aspect))) +
  geom_bar() +
  xlab("Model Aspect") +
  ylab("Count") +
  ggtitle("Model Aspect Distribution")

ggplot(clickstream, aes(x = factor(product_color))) +
  geom_bar() +
  xlab("Color") +
  ylab("Count") +
  ggtitle("Color Distribution")

ggplot(clickstream, aes(x = factor(price_higher_than_avg))) +
  geom_bar() +
  xlab("Higher than Average Price") +
  ylab("Count") +
  ggtitle("Average Price Distribution")

ggplot(clickstream, aes(x = factor(product_location_horiz))) +
  geom_bar() +
  xlab("Product Location Horizontal") +
  ylab("Count") +
  ggtitle("Horizontal Location Distribution")

ggplot(clickstream, aes(x = factor(product_location_vert))) +
  geom_bar() +
  xlab("Product Location Vertical") +
  ylab("Count") +
  ggtitle("Vertical Location Distribution")
```
```{r}
head(clickstream)
```

```{r}
ggplot(clickstream, aes(x = product_location_on_page, y = price, colour = factor(product_category))) +
  geom_point() +
  xlab("Product Location on Page") +
  ylab("Price") +
  ggtitle("Price vs. Product Location on Page") +
  labs(colour = "Product Category")

ggplot(clickstream, aes(y = product_location_on_page, x = product_code, colour = factor(product_category))) +
  geom_point() +
  ylab("Product Location on Page") +
  xlab("Product") +
  ggtitle("Price vs. Product Location on Page") +
  labs(colour = "Product Category")

```

```{r}
ggplot(clickstream, aes(x = price)) +
  geom_histogram(binwidth = 5, fill = "blue", alpha = 0.7) +
  xlab("Price") +
  ylab("Frequency") +
  ggtitle("Distribution of Product Prices")
```

```{r}
double_click <- clickstream %>% 
  group_by(product_location_on_page, session_ID) %>%
  count() %>%
  filter(n>1)
double_click

double_click <- double_click %>%
  mutate(product_location_on_page = factor(product_location_on_page, 
                                           levels = c("top-left", "top-middle", "top-right", "bottom-left", "bottom-middle", "bottom-right")))

ggplot(double_click, aes(x=as.factor(product_location_on_page), y=n, fill=as.factor(product_location_on_page))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session") +
    # guides(fill = guide_legend(title = "Location"))
    theme(legend.position = "none")

```
```{r}
click_counts <- clickstream %>% 
  group_by(product_location_on_page, product_code, session_ID) %>%
  count()
click_counts

sessions_with_doubles <- click_counts %>%
  filter(n > 1) %>%
  ungroup()
sessions_with_doubles

sessions_per_location <- sessions_with_doubles %>%
  group_by(product_location_on_page) %>%
  summarise(sessions_with_duplicates = n())

sessions_per_location <- sessions_per_location %>%
  mutate(product_location_on_page = factor(product_location_on_page, 
                                           levels = c("top-left", "top-middle", "top-right", "bottom-left", "bottom-middle", "bottom-right")))
sessions_per_location

ggplot(sessions_per_location, aes(x = product_location_on_page, y = sessions_with_duplicates, fill = product_location_on_page)) +
  geom_bar(stat = "identity", alpha = 0.7) +
  xlab("Product Location on Page") +
  ylab("Number of Sessions with Duplicate Clicks") +
  labs(title = "Sessions with Duplicate Clicks per Product Location") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") + 
  ylim(0,35000)
```
```{r}
clickstream <- clickstream %>%
  mutate(product_location_on_page = factor(product_location_on_page, 
                                           levels = c("top-left", "top-middle", "top-right", "bottom-left", "bottom-middle", "bottom-right")))

total_clicks <- clickstream %>%
  group_by(product_location_on_page) %>%
  summarise(absolute_clicks = n())

# ggplot(clickstream, aes(x = factor(product_location_on_page), fill = product_location_on_page)) +
#   # geom_bar(fill = "product_location_on_page") +
#   xlab("Product Location on Page") +
#   ylab("Number of Clicks") +
#   ggtitle("Total Clicks by Product Location")

ggplot(total_clicks, aes(x = product_location_on_page, y = absolute_clicks, fill = product_location_on_page)) +
  geom_bar(stat = "identity", alpha = 0.7) +
  xlab("Product Location on Page") +
  ylab("Absolute Number of Clicks") +
  labs(title = "Total Number of Clicks per Location") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none")
```
```


```{r look at the number of clicks per location}
clickstream_gp_loc <- clickstream %>%
  group_by(session_ID, product_location_on_page) %>%
  count()

ggplot(clickstream_gp_loc, aes(x=as.factor(product_location_on_page), y=n, fill=as.factor(product_location_on_page))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session") +
    guides(fill = guide_legend(title = "Location"))
```
```{r look at the number of clicks per location}
clickstream_count <- clickstream %>%
  group_by(product_location_on_page) %>%
  summarize(n = n())

ggplot(clickstream_count, aes(x=as.factor(product_location_on_page), y=n, fill=as.factor(product_location_on_page))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session by Product Location", subtitle = "Boxplot of Counts") +
    guides(fill = guide_legend(title = "Location"))
```


```{r}
clickstream
```

```{r}
ggplot(clickstream, aes(x = product_code)) +
  geom_histogram(fill = "blue", alpha = 0.7, stat="count") +
  xlab("Product") +
  ylab("Frequency") +
  ggtitle("Distribution of Product Clicks")

ggplot(clickstream, aes(x = factor(product_location_on_page), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Clicks") +
  ggtitle("Number of Clicks for Product Categories Across Locations") +
  labs(fill = "Product Category")

ggplot(clickstream, aes(x = factor(product_location_on_page), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Clicks") +
  ggtitle("Number of Clicks for Product Color Across Locations") +
  labs(fill = "Product Color")

ggplot(clickstream, aes(x = factor(product_location_on_page), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Clicks") +
  ggtitle("Number of Clicks for Model Aspect Across Locations") +
  labs(fill = "Aspect")

ggplot(clickstream, aes(x = product_code)) +
  geom_histogram(fill = "blue", alpha = 0.7, stat="count") +
  xlab("Product") +
  ylab("Frequency") +
  ggtitle("Distribution of Product Clicks")


```
```{r}
product_freq <- clickstream %>%
  count(product_code) %>%
  rename(Frequency=n)

# Determine the bins for frequency, this is just an example, and you might need to adjust it
binwidth <- 500  # This is the width of each bin, adjust as needed
product_freq$FrequencyBin <- cut(product_freq$Frequency, breaks=seq(0, max(product_freq$Frequency), by=binwidth), include.lowest=TRUE, right=FALSE)

# Plot the binned data
ggplot(product_freq, aes(x = FrequencyBin)) +
  geom_bar(fill = "blue", alpha = 0.7) +  # geom_bar uses stat="count" by default which is what we need
  xlab("Frequency Bin") +
  ylab("Count of Products") +
  ggtitle("Distribution of Product Clicks by Frequency Bin") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  # Rotate the x-axis text if it's overlapping
```


```{r}
clickstream %>%
  group_by(product_code, product_location_on_page) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

```
```{r}
clicks_by_location <- clickstream %>%
  group_by(product_location_on_page) %>%
  summarize(number_of_clicks = n())

clicks_by_location
```
```{r}
clickstream$z_score <- (clickstream$price - mean(clickstream$price, na.rm = TRUE)) / sd(clickstream$price, na.rm = TRUE)
outliers_z <- subset(clickstream, z_score > 3 | z_score < -3)
outliers_z
```

```{r number of products per location}

products_per_location <- clickstream %>%
  group_by(product_location_on_page) %>%
  summarise(number_of_products = n_distinct(product_code))
products_per_location

ggplot(products_per_location, aes(x = factor(product_location_on_page), y = number_of_products, fill = factor(product_location_on_page))) +
  geom_bar(stat = "identity", fill = "blue") +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products by Product Location") +
  theme_minimal() +
  theme(legend.position = "none")

```

```{r}
# ANOVA
anova_result <- aov(number_of_clicks ~ factor(product_location_on_page), data = clicks_by_location)
summary(anova_result)

# Kruskal-Wallis
kruskal_result <- kruskal.test(number_of_clicks ~ factor(product_location_on_page), data = clicks_by_location)
kruskal_result


```


```{r}
clickstream
```
```{r}
clickstream_filtered <- clickstream %>%
  filter(page_of_product == 1, country %in% c(4, 5, 6, 19, 21, 38, 41, 42), price_higher_than_avg == "no")
clickstream_filtered
```

```{r}

clicks_grouped_by_location <- clickstream_filtered %>%
  group_by(product_location_on_page, country, product_category, product_color,  product_image_model_aspect) %>%
  summarize(number_of_clicks = n())

clicks_grouped_by_location
```

```{r}

model <- lm(log(number_of_clicks) ~ factor(product_location_on_page) + country + product_category + product_color + product_image_model_aspect, data = clicks_grouped_by_location)
summary(model)

```
```{r}
clicks_grouped_by_location_price <- clickstream_filtered %>%
  group_by(price, product_location_on_page, country, product_category, product_color,  product_image_model_aspect) %>%
  summarize(number_of_clicks = n())

clicks_grouped_by_location_price
```

```{r}

model <- lm(number_of_clicks ~ price + country + product_category + product_color + product_image_model_aspect, data = clicks_grouped_by_location_price)
summary(model)

```
```{r}
clickstream
```

```{r Filtering and splitting data}
exp_clickstream_session <- clickstream  %>%
  group_by(session_ID, price_higher_than_avg, product_code, product_category, product_location_horiz, product_location_vert, 
           page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

exp_clickstream_session$n[exp_clickstream_session$n > 1] <- '1'

exp_clickstream_session <- exp_clickstream_session %>% 
        rename("total_clicks" = "n")

exp_clickstream_session <- tibble::rowid_to_column(exp_clickstream_session, "index")
ind = sample.split(Y = exp_clickstream_session$index, SplitRatio = 0.7)

# sub-setting into exploration data
exp_clickstream_session = exp_clickstream_session[!ind,]

exp_clickstream_session_prod <- exp_clickstream_session %>%
    group_by(price_higher_than_avg, product_code, product_category, product_location_horiz, product_location_vert, 
             page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

exp_clickstream_session_prod <- exp_clickstream_session_prod %>% 
        rename("total_clicks" = "n")

exp_clickstream_session_prod <- exp_clickstream_session_prod %>%
  filter(price_higher_than_avg == 'no')

exp_clickstream_session_prod <- subset(exp_clickstream_session_prod, select = -price_higher_than_avg)

exp_clickstream_session_prod

```
```{r}
# predictors <- as.formula("total_clicks ~ product_location_vert + product_location_horiz + product_color + price + product_image_model_aspect + product_category + page_of_product")
```

```{r}

model <- lm("total_clicks ~ product_location_vert + product_location_horiz + product_color + price + product_image_model_aspect + product_category + page_of_product", data = exp_clickstream_session_prod)
box_model <- lm("total_clicks ~ 1", data = exp_clickstream_session_prod)
# boxcox_result <- boxcox(model, lambda = seq(-2, 2, by = 0.1))
boxcox_result <- boxcox(box_model)
boxcox_result

```
```{r}
lambda <- boxcox_result$x[which.max(boxcox_result$y)]
lambda
```

```{r}
# Apply the Box-Cox transformation
if(lambda == 0){
  y_transformed <- log(exp_clickstream_session_prod$total_clicks)
} else {
  y_transformed <- (exp_clickstream_session_prod$total_clicks^lambda - 1) / lambda
}
```


```{r}
transformed_model <- lm(y_transformed ~ product_location_vert + product_location_horiz + product_color + price + product_image_model_aspect + product_category + page_of_product, data = exp_clickstream_session_prod)

summary(transformed_model)

```
```{r Excluding outliers with Cooks Distance}
cooksd <- cooks.distance(transformed_model)
influential <- cooksd > (4/(nrow(exp_clickstream_session_prod) - length(coefficients(transformed_model))))
clickstream_clean <- exp_clickstream_session_prod[!influential, ]

lambda_optimal <- boxcox_result$x[which.max(boxcox_result$y)]
lambda_optimal

# Apply the Box-Cox transformation
if(lambda == 0){
  y_clean_transformed <- log(clickstream_clean$total_clicks)
} else {
  y_clean_transformed <- (clickstream_clean$total_clicks^lambda - 1) / lambda_optimal
}

model_clean <- lm(y_clean_transformed ~ product_location_vert + product_location_horiz + product_color + price + product_image_model_aspect + product_category + page_of_product, data = clickstream_clean)
par(mfrow=c(2,2))
plot(model_clean)


```
```{r}
exp_clickstream_session_prod[influential, ]
```
```{r}
exp_clickstream_session_prod %>%
  filter(total_clicks<100)
```

```{r}
clickstream_clean
```

```{r Linearity}
plot(model, which = 1)
plot(transformed_model, which = 1)
plot(model_clean, which = 1)
```
```{r Independence - we have independence}
dwtest(model)
dwtest(transformed_model)
dwtest(model_clean)
```

```{r Homoscedasticity - Lookin good}
bptest(model)
bptest(transformed_model)
bptest(model_clean)

plot(model, which = 3)
plot(transformed_model, which = 3)
plot(model_clean, which = 3)
```

```{r Normality}
shapiro.test(residuals(model))
shapiro.test(residuals(transformed_model))
shapiro.test(residuals(model_clean))

ks.test(residuals(model), "pnorm", mean(residuals(model)), sd(residuals(model)))
ks.test(residuals(transformed_model), "pnorm", mean(residuals(transformed_model)), sd(residuals(transformed_model)))
ks.test(residuals(model_clean), "pnorm", mean(residuals(model_clean)), sd(residuals(model_clean)))

qqnorm(residuals(model))
qqline(residuals(model))

qqnorm(residuals(transformed_model))
qqline(residuals(transformed_model))

qqnorm(residuals(model_clean))
qqline(residuals(model_clean))

hist(residuals(model))
hist(residuals(transformed_model))
hist(residuals(model_clean))
```

