```{r load the libraries}
#install.packages("psych", dependencies=TRUE)
#install.packages("moments", dependencies=TRUE)
#install.packages("cowplot")
#install.packages("olsrr")
#install.packages("caTools")
#install.packages("fastDummies")

library(tidyr)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(lmtest)
library(psych)
library(moments)
library(tidyverse)
library(car)
library(cowplot)
library(olsrr)
library(caTools)
library(fastDummies)
library(MASS)
```

# EDA

```{r load the data}
clickstream_raw <- read.csv('e-shop clothing 2008.csv', sep =';', header = TRUE)
```

```{r look at the dimensions of the data}
dim(clickstream_raw)
```

There 165,474 different clicks
Each of the clicks have 14 different fields associated

```{r what are the names of the columns}
names(clickstream_raw)
```

```{r update the names of the columns to better represent the data represented}
clickstream <- clickstream_raw %>% 
        rename("sequence_click_in_session" = "order",
               "session_ID" = "session.ID",
               "product_category" = "page.1..main.category.",
               "product_code" = "page.2..clothing.model.",
               "product_color" = "colour",
               "product_location_on_page" = "location",
               "product_image_model_aspect" = "model.photography",
               "price_higher_than_avg" = "price.2",
               "page_of_product" = "page")


clickstream['product_location_vert'] <- clickstream['product_location_on_page']
clickstream['product_location_horiz'] <- clickstream['product_location_on_page']

clickstream <- clickstream %>%
  mutate(
    product_category = case_when(
      product_category == 1 ~ "Trousers",
      product_category == 2 ~ "Skirts",
      product_category == 3 ~ "Blouses",
      product_category == 4 ~ "Sale",
      TRUE ~ "Other"  # Default case
    ),
    product_image_model_aspect = case_when(
      product_image_model_aspect == 1 ~ "en face",
      product_image_model_aspect == 2 ~ "profile",
      TRUE ~ "Other"
    ),
    product_color = case_when(
      product_color == 1 ~ "beige",
      product_color == 2 ~ "black",
      product_color == 3 ~ "blue",
      product_color == 4 ~ "brown",
      product_color == 5 ~ "burgundy",
      product_color == 6 ~ "gray",
      product_color == 7 ~ "green",
      product_color == 8 ~ "navy blue",
      product_color == 9 ~ "of many colors",
      product_color == 10 ~ "olive",
      product_color == 11 ~ "pink",
      product_color == 12 ~ "red",
      product_color == 13 ~ "violet",
      product_color == 14 ~ "white",
      TRUE ~ "Other"
    ),
    price_higher_than_avg = case_when(
      price_higher_than_avg == 1 ~ "yes",
      price_higher_than_avg == 2 ~ "no",
      TRUE ~ "Other"
    ),
    product_location_horiz = case_when(
      product_location_horiz == 1 ~ 'left',
      product_location_horiz == 2 ~ 'middle',
      product_location_horiz == 3 ~ 'right',
      product_location_horiz == 4 ~ 'left',
      product_location_horiz == 5 ~ 'middle',
      product_location_horiz == 6 ~ 'left'
    ),
    product_location_vert = case_when(
      product_location_vert == 1 ~ 'top',
      product_location_vert == 2 ~ 'top',
      product_location_vert == 3 ~ 'top',
      product_location_vert == 4 ~ 'bottom',
      product_location_vert == 5 ~ 'bottom',
      product_location_vert == 6 ~ 'bottom'
    ),
    product_location_on_page = case_when(
      product_location_on_page == 1 ~ 'top-left',
      product_location_on_page == 2 ~ 'top-middle',
      product_location_on_page == 3 ~ 'top-right',
      product_location_on_page == 4 ~ 'bottom-left',
      product_location_on_page == 5 ~ 'bottom-middle',
      product_location_on_page == 6 ~ 'bottom-right'
    ),
    page_of_product = case_when(
      page_of_product == 1 ~ "first",
      page_of_product == 2 ~ "second",
      page_of_product == 3 ~ "third",
      page_of_product == 4 ~ "fourth",
      page_of_product == 5 ~ "fifth"
    )
    
  )
```

```{r look at the number of clicks per location to see if there are any outlier issues in the data}

clickstream_gp_loc <- clickstream %>%
  group_by(session_ID, product_location_on_page) %>%
  count()

ggplot(clickstream_gp_loc, aes(x=as.factor(product_location_on_page), y=n, fill=as.factor(product_location_on_page))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session") +
    guides(fill = guide_legend(title = "Location on Page"))

clickstream_gp_loc_2 <- clickstream %>%
  group_by(session_ID, product_location_horiz) %>%
  count()

ggplot(clickstream_gp_loc_2, aes(x=as.factor(product_location_horiz), y=n, fill=as.factor(product_location_horiz))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session") +
    guides(fill = guide_legend(title = "Horizontal Location"))

clickstream_gp_loc_3 <- clickstream %>%
  group_by(session_ID, product_location_vert) %>%
  count()

ggplot(clickstream_gp_loc_3, aes(x=as.factor(product_location_vert), y=n, fill=as.factor(product_location_vert))) +
    geom_boxplot(alpha=0.2) +
    xlab("Location of Product Clicked") +
    ylab("Number of Clicks per Session") +
    labs(title = "Distribution of Clicks per Session") +
    guides(fill = guide_legend(title = "Verticle Location"))
```

Data demonstrates that there's several outliers in the multiple clicks in a single session for those products on the left. The analysis is looking at initial clicks not repeat clicks.

```{r only count the first click in a session}
clickstream_session <- clickstream  %>%
  group_by(session_ID, price_higher_than_avg, product_code, product_category, product_location_on_page, 
           product_location_horiz, product_location_vert, page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

sum(clickstream_session$n > 1)

clickstream_session$n[clickstream_session$n > 1] <- '1'

clickstream_session <- clickstream_session %>% 
        rename("total_clicks" = "n")
```

```{r group the entire dataset for analysis}
clickstream_session_prod <- clickstream_session %>%
    group_by(price_higher_than_avg, product_code, product_category, product_location_on_page, product_location_horiz, 
             product_location_vert, page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

clickstream_session_prod <- clickstream_session_prod %>% 
        rename("total_clicks" = "n")
```


```{r look at basic analytic graphs on the dataset - distribution of clicks per session based on features}

ggplot(clickstream_session, aes(x = factor(product_location_on_page))) +
  geom_bar(fill = "blue") +
  xlab("Product Location on Page") +
  ylab("Number of Unique Clicks per Session") +
  ggtitle("Total Unique Clicks per Session by Product Location")

ggplot(clickstream_session, aes(x = factor(product_location_horiz))) +
  geom_bar(fill = "blue") +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Unique Clicks per Session") +
  ggtitle("Total Unique Clicks per Session by Product Location, Horizontal")

ggplot(clickstream_session, aes(x = factor(product_location_vert))) +
  geom_bar(fill = "blue") +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Unique Clicks per Session") +
  ggtitle("Total Unique Clicks per Session by Product Location, Vertical")

ggplot(clickstream_session, aes(x = product_code)) +
  geom_histogram(fill = "blue", alpha = 0.7, stat="count") +
  xlab("Product") +
  ylab("Frequency") +
  ggtitle("Distribution of Product Clicks")
```

```{r look at basic analytic graphs on the dataset - distribution of products based on non-location features}
ggplot(clickstream_session_prod, aes(x = factor(page_of_product))) +
  geom_bar(fill = 'red') +
  xlab("Page of product") +
  ylab("Number of Products") +
  ggtitle("Number of Products for per Page") +
  labs(fill = "Product Page")

ggplot(clickstream_session_prod, aes(x = factor(product_category))) +
  geom_bar(fill = 'red') +
  xlab("Product Category") +
  ylab("Count of Products") +
  ggtitle("Product Category Distribution")

ggplot(clickstream_session_prod, aes(x = factor(product_image_model_aspect))) +
  geom_bar(fill = 'red') +
  xlab("Model Aspect") +
  ylab("Count of Products") +
  ggtitle("Model Aspect Distribution")

ggplot(clickstream_session_prod, aes(x = factor(product_color))) +
  geom_bar(fill = 'red') +
  xlab("Color") +
  ylab("Count of Products") +
  ggtitle("Color Distribution")
```

```{r look at basic analytic graphs on the dataset - distribution of products based on location features}
ggplot(clickstream_session_prod, aes(x = factor(product_location_on_page))) +
  geom_bar(fill = "blue") +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location")

ggplot(clickstream_session_prod, aes(x = factor(product_location_horiz))) +
  geom_bar(fill = "blue") +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location, Horizontal")

ggplot(clickstream_session_prod, aes(x = factor(product_location_vert))) +
  geom_bar(fill = "blue") +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location, Vertical")

```

```{r look at basic analytic graphs on the dataset - distribution of products based on location & features}
ggplot(clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations") +
  labs(fill = "Product Category")

ggplot(clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations, Horizontal") +
  labs(fill = "Product Category")

ggplot(clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations, Vertical") +
  labs(fill = "Product Category")

ggplot(clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations") +
  labs(fill = "Product Color")

ggplot(clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations, Horizontal") +
  labs(fill = "Product Color")

ggplot(clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations, Vertical") +
  labs(fill = "Product Color")

ggplot(clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations") +
  labs(fill = "Aspect")

ggplot(clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations, Horizontal") +
  labs(fill = "Aspect")

ggplot(clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations, Vertical") +
  labs(fill = "Aspect")
```

```{r split the data into an exploration and a confirmation dataset}

# create an index to allow you to spit the data
#clickstream_session <- tibble::rowid_to_column(clickstream_session, "index")

# create your breakdown
#ind = sample.split(Y = clickstream_session$index, SplitRatio = 0.7)

# sub-setting into exploration data
#exp_clickstream_session = clickstream_session[!ind,]

# sub-setting into confirmation data
#conf_clickstream_session = clickstream_session[ind,]

# export the datasets to maintain consistency in our analytics
#write.csv(exp_clickstream_session, "exp_clickstream_session_new.csv", row.names=TRUE)
#write.csv(conf_clickstream_session, "conf_clickstream_session_new.csv", row.names=TRUE)
```

```{r load the saved dataset }
exp_clickstream_session <- read.csv('exp_clickstream_session.csv', sep =',', header = TRUE)
conf_clickstream_session <- read.csv('conf_clickstream_session.csv', sep =',', header = TRUE)
```

```{r group each of the subsets by product}

# group the exploration dataset
exp_clickstream_session_prod <- exp_clickstream_session %>%
    group_by(price_higher_than_avg, product_code, product_category, product_location_on_page, product_location_horiz, 
             product_location_vert, page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

exp_clickstream_session_prod <- exp_clickstream_session_prod %>% 
        rename("total_clicks" = "n")

# group the confirmation dataset
conf_clickstream_session_prod <- conf_clickstream_session %>%
    group_by(price_higher_than_avg, product_code, product_category, product_location_on_page, product_location_horiz, 
             product_location_vert, page_of_product, price, product_color, product_image_model_aspect) %>%
  count(product_code)

conf_clickstream_session_prod <- conf_clickstream_session_prod %>% 
        rename("total_clicks" = "n")
```

Y = 'total_clicks'
X = 'product_location' ('product_location_vert' + 'product_location_horiz')
Covariates = product_category, product_color, product_image_model_aspect, page_of_product

Of note, we did consider price as a covariate but given price is not actually something that is displayed, we did not identify it as a covariate since the user cannot SEE it.

Controls = we considered controlling for the page, but we did not have enough data to control for that (i.e. at most only 70 products are in each page). 

```{r provide a description of the exploration dataset}
describe(exp_clickstream_session_prod)
```

```{r look at a summary of the exploration dataset}
summary(exp_clickstream_session_prod)
```

```{r look at basic analytic graphs on the exploration dataset}

ggplot(exp_clickstream_session_prod, aes(x = factor(page_of_product))) +
  geom_bar(fill = 'red') +
  xlab("Page of product") +
  ylab("Number of Products") +
  ggtitle("Number of Products for per Page") +
  labs(fill = "Product Page")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_category))) +
  geom_bar(fill = 'red') +
  xlab("Product Category") +
  ylab("Count of Products") +
  ggtitle("Product Category Distribution")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_image_model_aspect))) +
  geom_bar(fill = 'red') +
  xlab("Model Aspect") +
  ylab("Count of Products") +
  ggtitle("Model Aspect Distribution")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_color))) +
  geom_bar(fill = 'red') +
  xlab("Color") +
  ylab("Count of Products") +
  ggtitle("Color Distribution")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_on_page))) +
  geom_bar(fill = "blue") +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_horiz))) +
  geom_bar(fill = "blue") +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location, Horizontal")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_vert))) +
  geom_bar(fill = "blue") +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Total Products by Product Location, Vertical")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations") +
  labs(fill = "Product Category")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations, Horizontal") +
  labs(fill = "Product Category")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_category))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Categories Across Locations, Vertical") +
  labs(fill = "Product Category")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations") +
  labs(fill = "Product Color")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations, Horizontal") +
  labs(fill = "Product Color")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_color))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Product Color Across Locations, Vertical") +
  labs(fill = "Product Color")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_on_page), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations") +
  labs(fill = "Aspect")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_horiz), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Horizontal Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations, Horizontal") +
  labs(fill = "Aspect")

ggplot(exp_clickstream_session_prod, aes(x = factor(product_location_vert), fill = factor(product_image_model_aspect))) +
  geom_bar(position = position_dodge()) +
  xlab("Product Vertical Location on Page") +
  ylab("Number of Products") +
  ggtitle("Number of Products for Model Aspect Across Locations, Vertical") +
  labs(fill = "Aspect")
```

```{r conduct a boxcox test to identify what transformations are best for the total unique clicks}

b <- boxcox(lm(exp_clickstream_session_prod$total_clicks ~ 1))

# this provides the exact number from the boxcox test that we should raise to the power of
lambda <- b$x[which.max(b$y)]
lambda

# tests if we can reject the null hypothesis of normality ... which we cannot under the transformation
test_lambda <- exp_clickstream_session_prod$total_clicks^lambda
shapiro.test(test_lambda)

# if you test the null hypothesis with the other options of log, sqrt etc
test_log <- log(exp_clickstream_session_prod$total_clicks)
shapiro.test(test_log)

test_sqrt <- sqrt(exp_clickstream_session_prod$total_clicks)
shapiro.test(test_sqrt)
```

```{r create a histogram for the distribution of the total clicks per product}
c_hist<-exp_clickstream_session_prod %>%
  ggplot(aes(x=total_clicks)) +
  geom_histogram(bins=30) +
  labs(
    x = "Total # of Clicks per Product",
    title = "Distribution of Clicks per Product"
  )

p_hist<-exp_clickstream_session_prod %>%
  ggplot(aes(x=price)) +
  geom_histogram(bins=8) +
  labs(
    x = "Price of Product",
    title = "Distribution of Product Price"
  )

c_hist_log<-exp_clickstream_session_prod %>%
  ggplot(aes(x = log(total_clicks))) +
  geom_histogram() +
  labs(
    x = 'Ln(Total Clicks)',
    title = "Distribution of ln(Total Clicks per Product)"
  )

p_hist_log<-exp_clickstream_session_prod %>%
  ggplot(aes(x = log(price))) +
  geom_histogram() +
  labs(
    x = "Ln(Price)",
    title = "Distribution of ln(Product Price)"
  )

c_hist_sr<-exp_clickstream_session_prod %>%
  ggplot(aes(x = sqrt(total_clicks))) +
  geom_histogram() +
  labs(
    x = 'Sqrt(Total Clicks)',
    title = "Distribution of Sqrt(Total Clicks per Product)"
  )

c_hist_lambda<-exp_clickstream_session_prod %>%
  ggplot(aes(x = (total_clicks^lambda))) +
  geom_histogram() +
  labs(
    x = 'Total Clicks^Lambda',
    title = "Distribution of Total Clicks per Product^Lambda"
  )
```


```{r evaluate the qq norm plots for the key variables}
qqclicks<-ggplot(exp_clickstream_session_prod,aes(sample=total_clicks)) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="Total # of Clicks per Product", title = "qqnormal plot of total clicks")

qqprice<-ggplot(exp_clickstream_session_prod,aes(sample=price)) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="Product Price", title = "qqnormal plot of product price")

qqclicks_ln<-ggplot(exp_clickstream_session_prod,aes(sample=log(total_clicks))) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="ln(total clicks)", title = "qqnormal plot of ln(total clicks per product)")

qqprice_ln<-ggplot(exp_clickstream_session_prod,aes(sample=log(price))) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="ln(price)", title = "qqnormal plot of ln(product price)")

qqclicks_sr<-ggplot(exp_clickstream_session_prod,aes(sample=sqrt(total_clicks))) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="sqrt(total clicks)", title = "qqnormal plot of sqrt(total clicks per product)")

qqclicks_lambda<-ggplot(exp_clickstream_session_prod,aes(sample=(total_clicks^lambda))) + geom_qq(distribution=qnorm) +
  geom_qq_line(line.p = c(0.25, 0.75), col = "blue") + labs(y="Total clicks^Lambda", title = "qqnormal plot of (total clicks per product)^lambda")
```


```{r show the comparison charts for distribution}

options(repr.plot.width=7.5, repr.plot.height=2)
suppressWarnings(grid.arrange(c_hist, qqclicks, c_hist_log, qqclicks_ln, c_hist_sr, qqclicks_sr, c_hist_lambda, 
                              qqclicks_lambda, ncol = 2, padding = unit(0.1, 'line')))
                              
                              
suppressWarnings(grid.arrange(p_hist, qqprice, p_hist_log, qqprice_ln, ncol = 2, 
                              padding = unit(0.1, 'line')))


suppressWarnings(grid.arrange(qqclicks, qqclicks_lambda, ncol = 2, 
                              padding = unit(0.1, 'line')))
```

Assessment is that it would be good to log the total clicks, but does not appear to impact the distribution of the price. Also it still does not look like as good of a transformation for the total unique clicks as we'd like so do a boxcox test.

# Description of how to interpret stepped qq plots
https://stats.stackexchange.com/questions/161591/how-to-interpret-this-qq-plot

```{r relevel the data so that the base for location is top-left}
exp_clickstream_session_prod$product_location_on_page <- factor(exp_clickstream_session_prod$product_location_on_page)
exp_clickstream_session_prod$product_location_on_page <- relevel(exp_clickstream_session_prod$product_location_on_page, ref =
                                                                   'top-left')
```

```{r relevel the data so that the base for horiz location is left}
exp_clickstream_session_prod$product_location_horiz <- factor(exp_clickstream_session_prod$product_location_horiz)
exp_clickstream_session_prod$product_location_horiz <- relevel(exp_clickstream_session_prod$product_location_horiz, ref =
                                                                   'left')
```

```{r relevel the data so that the base for horiz location is top}
exp_clickstream_session_prod$product_location_vert <- factor(exp_clickstream_session_prod$product_location_vert)
exp_clickstream_session_prod$product_location_vert <- relevel(exp_clickstream_session_prod$product_location_vert, ref =
                                                                   'top')
```

```{r relevel the data so that the base for page is first}
exp_clickstream_session_prod$page_of_product <- factor(exp_clickstream_session_prod$page_of_product)
exp_clickstream_session_prod$page_of_product <- relevel(exp_clickstream_session_prod$page_of_product, ref =
                                                                   'first')
```

```{r create a model that uses only product location}
model1 <- lm((total_clicks^lambda) ~ product_location_on_page + page_of_product + product_category, data = 
               exp_clickstream_session_prod)
anova(model1)
summary(model1)
```

```{r look at a model that now includes location based on horiz vs vert}
model2 <- lm((total_clicks^lambda) ~ product_location_horiz + product_location_vert, data = exp_clickstream_session_prod)

anova(model2)
summary(model2)
```


```{r remove outliers of our total clicks per product based on cooks distance}
# need to ensure this works -- need to redo the transformed model section
cooksd <- cooks.distance(model1)
influential <- cooksd > (4/(nrow(exp_clickstream_session_prod) - length(coefficients(model1))))
exp_clickstream_session_prod_no_outliers <- exp_clickstream_session_prod[!influential, ]
```

```{r re-run and get the best lambda based on removal of the outliers}
# need to redo this as well
b_new <- boxcox(lm(exp_clickstream_session_prod_no_outliers$total_clicks ~ 1))

# this provides the exact number from the boxcox test that we should raise to the power of
lambda_optimal <- b_new$x[which.max(b_new$y)]
lambda_optimal

# tests if we can reject the null hypothesis of normality ... which we cannot under the transformation
test_lambda_new <- exp_clickstream_session_prod_no_outliers$total_clicks^lambda_optimal
shapiro.test(test_lambda)

# if you test the null hypothesis with the other options of log, sqrt etc
test_log_new <- log(exp_clickstream_session_prod_no_outliers$total_clicks)
shapiro.test(test_log_new)

test_sqrt_new <- sqrt(exp_clickstream_session_prod_no_outliers$total_clicks)
shapiro.test(test_sqrt_new)
```

```{r evalaute the colinearity of the variables using a pairplot}
#suppressWarnings(scatterplotMatrix(~log(exp_clickstream_prod$total_clicks) + exp_clickstream_prod$product_location_on_page +
                                     #exp_clickstream_prod$product_category + exp_clickstream_prod$page_of_product + 
                                     #exp_clickstream_prod$price + exp_clickstream_prod$product_color + 
                                     #exp_clickstream_prod$product_image_model_aspect,data = exp_clickstream_prod,  
                                   #plot.points = F, smoother=loessLine))
```

```{r create a model that uses each of the specific dummy variables wout the outliers}
model3 <- lm((total_clicks^lambda_optimal) ~ product_location_on_page + page_of_product + product_category, data = 
               exp_clickstream_session_prod_no_outliers)
  
anova(model3)
summary(model3)
```

# This is for our actual model

```{r relevel the data so that the base for location is top-left}
conf_clickstream_session_prod$product_location_on_page <- factor(conf_clickstream_session_prod$product_location_on_page)
conf_clickstream_session_prod$product_location_on_page <- relevel(conf_clickstream_session_prod$product_location_on_page, ref
                                                                  = 'top-left')
```

```{r relevel the data so that the base for page is first}
conf_clickstream_session_prod$page_of_product <- factor(conf_clickstream_session_prod$page_of_product)
conf_clickstream_session_prod$page_of_product <- relevel(conf_clickstream_session_prod$page_of_product, ref =
                                                                   'first')
```

```{r calculate the final model with the confirmation dataset with just our variable}
model_final_loc <- lm((total_clicks^lambda_optimal) ~ product_location_on_page, data = 
               conf_clickstream_session_prod)
  
anova(model_final_loc)
summary(model_final_loc)
```


```{r calculate the final model with the confirmation dataset with the variables we know we want}
model_final <- lm((total_clicks^lambda_optimal) ~ product_location_on_page + page_of_product + product_category, data = 
               conf_clickstream_session_prod)
  
anova(model_final)
summary(model_final)
```

```{r calculate the final model with the confirmation dataset with the variables}
model_kitchen_sink <- lm((total_clicks)^(lambda_optimal) ~ product_location_on_page + page_of_product + product_category + price + product_color + product_image_model_aspect + price_higher_than_avg, data = conf_clickstream_session_prod)

anova(model_kitchen_sink)
summary(model_kitchen_sink)
```
```{r CLM -  normality of residuals}

plot(model_final, which = 1)
shapiro.test(sample(model_final$residuals))
jarque.test(model_final$residuals)
```
```{r CLM - 1 normality of residuals}

plot(model_final, which = 2)
shapiro_residuals <- shapiro.test(sample(model_final$residuals))
jarque_residuals <- jarque.test(model_final$residuals)

skewness <- skewness(model_final$residuals)
k_val <- kurtosis(model_final$residuals) - 3

shapiro_residuals
jarque_residuals
skewness
k_val

# fairly clear that there remain issues with outliers; reject the null hypothesis of normality in the residual errors
# left skewed with an extremely high kurtosis
```

```{r CLM - 2 homoscedastic errors}
plot(model_final, which = 3)
bptest <- bptest(model_final)
bptest

# ocular shows that the squared standard residual error is around .76; the p-value is not lower than 0.05, so the model fails to reject the null hypothesis that there is no evidence for heteroscedastic error. So, there is no evidence of heteroscedastic errors.
```

```{r CLM - 3 linear conditional expecations}
plot(model_final, which = 1)
ols_plot_resid_hist(model_final)
quantile <- summary(model_final$residuals)
quantile
```

```{r CLM - 4 evaluate colinarity by looking at the VIF model}
vif(model_final)
# given they're all close to 1, you can assess that they are not correlated
```

```{r CLM - 5 evaluate IID}
#install.packages("dgof")
#library(dgof)
ks.test(conf_clickstream_session_prod)
```


